\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-12-18 archive.tex
shorten some equations (vs section)

\begin{figure}
  \begin{tikzpicture}[line width=0.4mm]
    \draw[fill=white] (-1,1) -- (13,1) -- (13,-4) -- (-1,-4) -- (-1,1);
    \node at (5.5,1.25) {\textsc{\textbf{Wake}}};

@@

    \node at (0.5,-4.75) {\textbf{\textsc{Sleep: Consolidation}}};
    \draw (-2,-5) -- (3,-5) -- (3,-10) -- (5.5,-10) -- (5.5,-13) -- (-2,-13) -- (-2,-5);
    \node at (11.5,-4.75) {\textbf{\textsc{Sleep: Dreaming}}};
    \draw (14,-5) -- (9,-5) -- (9,-10) -- (6.5,-10) -- (6.5,-13) -- (14,-13) -- (14,-5);

@@

@@

@@

\textbf{Idea 2:} Rather than explicitly enumerate every refactoring,
we developed a technique for compactly representing and efficiently
calculating the set of all refactorings.  The key idea is to represent
the set of refactorings using a \emph{version
  space}~\cite{lau2001programming,mitchell1977version,polozov2015flashmeta}.
A version space is a tree-shaped data structure
that compactly represents a large set of programs.
We first define version spaces over $\lambda$-calculus expressions,
and then give a dynamic program for constructing a version space
that represents the set of possible refactorings (i.e., $R_n(p)$).
This technique is astronomically more efficient than
explicitly representing
the space of possible refactorings:
for the example in Figure~\ref{mapFactor},
we represent
the space of refactorings using a version space with
$10^6$ nodes,
which encodes $10^{14}$ refactorings.
Formally, a version space is either:
\begin{itemize}
\item A deBuijn\footnote{deBuijn indices are an alternative way of naming variables in $\lambda$-calculus. When using deBuijn indices, $\lambda$-abstractions are written \emph{without} a variable name, and variables are written as the count of the number of $\lambda$-abstractions up in the syntax tree the variable is bound to. For example, $\lambda x.\lambda y. (x\;y)$ is written $\lambda\lambda (\$1\;\$0)$ using deBuijn indices. See~\cite{pierce} for more details.} index: written $\$i$, where $i$ is a natural number
\item An abstraction: written $\lambda v$, where $v$ is a version space
\item An  application: written $(f \;x)$, where both  $f$ and $x$ are version spaces
\item A  union: $\uplus V$, where $V$ is a set of version spaces
\item The empty set, $\varnothing$
\item The set of all $\lambda$-calculus expressions, $\Lambda$
\end{itemize}
The purpose of a version space to compactly represent a set of programs.
We refer to this set as the \textbf{extension} of the version space:
\begin{definition}
  The \textbf{extension} of a version space $v$ is written $\denotation{v}$
  and is defined recursively as:
  \begin{align*}
    \denotation{\$i}& = \left\{\$i \right\}&
    \denotation{\lambda v}& = \left\{\lambda e : e\in \denotation{v} \right\}&
    \denotation{(v_1\; v_2)}& = \left\{(e_1\;e_2) : e_1\in \denotation{v_1},\;e_2\in \denotation{v_2} \right\}\\
    \denotation{\uplus V}& = \left\{e : v\in V,\;e\in \denotation{v} \right\}&
    \denotation{\varnothing}& = \varnothing&
    \denotation{\Lambda}& = \Lambda
    \end{align*}
\end{definition}
Version spaces also support efficient membership checking, which we
write as  $e\in \denotation{v}$.
Important for our purposes, it is also efficient to refactor the
members of a version space's extension in terms of a new DSL.
We define $\textsc{refactor}(v|\mathcal{D})$ inductively as:
\begin{align}
  \textsc{refactor}(v|\mathcal{D}) &= \begin{cases}
    e\text{, if $e\in \mathcal{D}$ and $e\in \denotation{v}$. Exploits the fact that $\denotation{e}\in v$ can be efficiently computed.}\\
    \textsc{refactor}'(v|\mathcal{D})\text{, otherwise.}
  \end{cases}\label{FACTORING}\\\nonumber    
  \textsc{refactor}'(e|\mathcal{D})& = e\text{, if $e$ is a leaf}&%\\\nonumber
  \textsc{refactor}'(\lambda b|\mathcal{D}) &= \lambda \textsc{refactor}(b|\mathcal{D})\\\nonumber
  \textsc{refactor}'(f\;x|\mathcal{D}) &= \textsc{refactor}(f|\mathcal{D})\;\textsc{refactor}(x|\mathcal{D})&%\\\nonumber
  \textsc{refactor}'(\uplus V|\mathcal{D}) &= \argmin_{e\in \left\{\textsc{refactor}(v|\mathcal{D})\;:\;v\in V \right\}}\text{size}(e|\mathcal{D})\nonumber
  \end{align*}
where $\text{size}(e|\mathcal{D})$ for program $e$ and DSL $\mathcal{D}$
is the size of the syntax tree of $e$,
when members of $\mathcal{D}$ are counted as having size 1.
Concretely, $  \textsc{refactor}(v|\mathcal{D})$ calculates $\argmin_{p\in \denotation{v}}\text{size}(p|\mathcal{D})$.

>>>>

\begin{figure}
  \begin{tikzpicture}[line width=0.4mm]
    \draw[fill=teal!5!white] (-1,1) -- (13,1) -- (13,-4) -- (-1,-4) -- (-1,1);
    \node at (5.5,1.25) {\textsc{\textbf{Wake}}};

@@

    \node at (0.5,-4.75) {\textbf{\textsc{Sleep: Consolidation}}};
    \draw[fill=teal!5!white] (-2,-5) -- (3,-5) -- (3,-10) -- (5.5,-10) -- (5.5,-13) -- (-2,-13) -- (-2,-5);
    \node at (11.5,-4.75) {\textbf{\textsc{Sleep: Dreaming}}};
    \draw[fill=teal!5!white] (14,-5) -- (9,-5) -- (9,-10) -- (6.5,-10) -- (6.5,-13) -- (14,-13) -- (14,-5);

@@

    \draw (-2,-2.5) -- (15,-2.5);
    \node[align=left] at (-1.5,-2.3) {Tasks and\\\texttt{Programs}\\\\DSL};

@@

    \node(appendSingle)[draw, rounded corners, align=center,text width=2.5cm] at ([yshift=-2cm]delimited.center) {
      \code{$f_7($c$,$s$)\,=\,$}\\
      \mcode{($f_1$ (cons c empty) s)}};
    \node[anchor = north] at (appendSingle.south) {append character};

    \node(surround)[draw, rounded corners, align=center,text width=2.5cm] at ([yshift=-2cm]appendSingle.center) {
      \code{$f_8($s$)\,=\,$}\\
      \mcode{(cons \codechar{(} ($f_7$ \codechar{)} s))}};
    \node[anchor = north] at (surround.south) {surround in parentheses};
    \draw[->] (surround.west) to[in=200,out=160] ([yshift=-0.25cm]appendSingle.west);
    \draw[->] (appendSingle.west) to[in=40,out=120] ([yshift=0.25cm]cat.east);

@@

\textbf{Idea 2:} Rather than explicitly enumerate every refactoring,
we developed a technique for compactly representing and efficiently
calculating the set of all refactorings.  The key idea is to represent
the set of refactorings using a \emph{version
  space}~\cite{lau2001programming,mitchell1977version,polozov2015flashmeta}.
A version space is a tree-shaped data structure
that compactly represents a large set of programs.
We first define version spaces over $\lambda$-calculus expressions,
and then give a dynamic program for constructing a version space
that represents the set of possible refactorings (i.e., $R_n(p)$).
This technique is astronomically more efficient than
explicitly representing
the space of possible refactorings:
for the example in Figure~\ref{mapFactor},
we represent
the space of refactorings using a version space with
$10^6$ nodes,
which encodes $10^{14}$ refactorings.
Formally, a version space is either:
\begin{itemize}
\item A deBuijn\footnote{deBuijn indices are an alternative way of naming variables in $\lambda$-calculus. When using deBuijn indices, $\lambda$-abstractions are written \emph{without} a variable name, and variables are written as the count of the number of $\lambda$-abstractions up in the syntax tree the variable is bound to. For example, $\lambda x.\lambda y. (x\;y)$ is written $\lambda\lambda (\$1\;\$0)$ using deBuijn indices. See~\cite{pierce} for more details.} index: written $\$i$, where $i$ is a natural number
\item An abstraction: written $\lambda v$, where $v$ is a version space
\item An  application: written $(f \;x)$, where both  $f$ and $x$ are version spaces
\item A  union: $\uplus V$, where $V$ is a set of version spaces
\item The empty set, $\varnothing$
\item The set of all $\lambda$-calculus expressions, $\Lambda$
\end{itemize}
The purpose of a version space to compactly represent a set of programs.
We refer to this set as the \textbf{extension} of the version space:
\begin{definition}
  The \textbf{extension} of a version space $v$ is written $\denotation{v}$
  and is defined recursively as:
  \begin{align*}
    \denotation{\$i}& = \left\{\$i \right\}&
    \denotation{\lambda v}& = \left\{\lambda e : e\in \denotation{v} \right\}&
    \denotation{(v_1\; v_2)}& = \left\{(e_1\;e_2) : e_1\in \denotation{v_1},\;e_2\in \denotation{v_2} \right\}\\
    \denotation{\uplus V}& = \left\{e : v\in V,\;e\in \denotation{v} \right\}&
    \denotation{\varnothing}& = \varnothing&
    \denotation{\Lambda}& = \Lambda
    \end{align*}
\end{definition}
Version spaces also support efficient membership checking, which we
write as  $e\in \denotation{v}$.
Important for our purposes, it is also efficient to refactor the
members of a version space's extension in terms of a new DSL.
We define $\textsc{refactor}(v|\mathcal{D})$ inductively as:
\begin{align*}
  \textsc{refactor}(v|\mathcal{D}) &= \begin{cases}
    e\text{, if $e\in \mathcal{D}$ and $e\in \denotation{v}$. Exploits the fact that $\denotation{e}\in v$ can be efficiently computed.}\\
    \textsc{refactor}'(v|\mathcal{D})\text{, otherwise.}
  \end{cases}
\end{align*}\vspace{-\baselineskip}%
\begin{align*}
  \textsc{refactor}'(e|\mathcal{D})& = e\text{, if $e$ is a leaf}&%\\\nonumber
  \textsc{refactor}'(\lambda b|\mathcal{D}) &= \lambda \textsc{refactor}(b|\mathcal{D})\\\nonumber
  \textsc{refactor}'(f\;x|\mathcal{D}) &= \textsc{refactor}(f|\mathcal{D})\;\textsc{refactor}(x|\mathcal{D})&%\\\nonumber
  \textsc{refactor}'(\uplus V|\mathcal{D}) &= \argmin_{e\in \left\{\textsc{refactor}(v|\mathcal{D})\;:\;v\in V \right\}}\text{size}(e|\mathcal{D})\nonumber
  \end{align*}
where $\text{size}(e|\mathcal{D})$ for program $e$ and DSL $\mathcal{D}$
is the size of the syntax tree of $e$,
when members of $\mathcal{D}$ are counted as having size 1.
Concretely, $  \textsc{refactor}(v|\mathcal{D})$ calculates $\argmin_{p\in \denotation{v}}\text{size}(p|\mathcal{D})$.
